\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-03 casestudies.tex
update
modified:   casestudies.tex 	modified:   intro.tex 	modified:   methodology.tex 	modified:   overview.tex 	modified:   paper.tex 	modified:   psharp.tex

% N.B. Artifact Services is mentioned at http://research.microsoft.com/en-us/people/schulte/.  Hopefully it's OK to reveal that it was the system in this case study. ~ Matt 2015-08-17
The initial motivation for MigratingTable was to solve a scaling problem for Artifact Services, an internal Microsoft system with a data set that is sharded across tables in different Azure storage accounts because it exceeds the limit on traffic supported by a single Azure storage account.  As the traffic continues to grow over time, we will need to reshard the data set across a greater number of Azure storage accounts without interrupting service.  During such a resharding, our sharding manager will identify each key range that should migrate to a different table, and we will use a separate MigratingTable instance for each such key range to actually perform the migration (Figure~\ref{fig:livemigration}).  MigratingTable may also be useful to migrate data to a table with different values of configuration parameters that Azure does not support changing on an existing table, such as geographic location.

\subsection{Azure Service Fabric (CScale?}
\label{sec:cases:fabric}

>>>>

% N.B. Artifact Services is mentioned at http://research.microsoft.com/en-us/people/schulte/.  Hopefully it's OK to reveal that it was the system in this case study. ~ Matt 2015-08-17
The initial motivation for MigratingTable was to solve a scaling problem for Artifact Services, an internal Microsoft system with a data set that is sharded across tables in different Azure storage accounts because it exceeds the limit on traffic supported by a single Azure storage account.  As the traffic continues to grow over time, we will need \SCComment{change to "the system needs", because the word "we" is unclear} to reshard the data set across a greater number of Azure storage accounts without interrupting service.  During such a resharding, our sharding manager will identify each key range that should migrate to a different table, and we will use a separate MigratingTable instance for each such key range to actually perform the migration (Figure~\ref{fig:livemigration}).  MigratingTable may also be useful to migrate data to a table with different values of configuration parameters that Azure does not support changing on an existing table, such as geographic location.

\subsection{Azure Service Fabric (change to CScale?)}
\label{sec:cases:fabric}

### 2015-09-03 intro.tex
modified:   casestudies.tex 	modified:   intro.tex 	modified:   methodology.tex 	modified:   overview.tex 	modified:   paper.tex 	modified:   psharp.tex

Distributed systems are notoriously hard to design, implement and test~\cite{cavage2013there, laguna2015debugging, maddox2015test}. This is due to many well-known sources of \emph{nondeterminism}~\cite{chandra2007paxos}, such as race conditions in the asynchronous interaction between system components, the use of multithreaded code inside a component, unexpected node failures, unreliable communication channels and data losses, and interaction with (human) clients.
%
All these sources of nondeterminism translate into \emph{exponentially} many execution paths that a distributed system might potentially execute. A bug might hide deep inside one of these paths and only manifest under extremely rare corner cases~\cite{gray1986computers, musuvathi2008finding}.

Classic techniques that product groups employ to test, verify and validate their systems (such as code reviews, unit testing, stress testing and fault injection) are unable to capture and control all the aforementioned sources of nondeterminism, which causes the most tricky bugs being missed during testing and only getting exposed after a system has been put in production. Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money and many dissatisfied customers.

We interviewed engineers from the Microsoft Azure team regarding the top problems in distributed system development, and the unified response was that the most critical problem today is how to improve \emph{testing coverage} to find bugs \emph{before} a system goes in production. The need for better testing techniques is not specific to Microsoft; other companies, such as Amazon and Google, publicly acknowledge~\cite{newcombe2015aws} that testing methodologies have to improve to be able to reason about the correctness of increasingly more complex distributed systems.

Amazon recently published an article~\cite{newcombe2015aws} that describes their use of TLA+~\cite{lamport1994temporal} to detect distributed system bugs and prevent them from reaching production. TLA+ is a powerful specification language for verifying distributed protocols, but it is unable to verify the code that is actually being executed. The implied assumption is that a model of the system will be verified, and then the programmers are responsible to match what was verified with the source code of the real system. Although many design bugs can be caught with this approach, there is \emph{no guarantee} that the real distributed system will be free of bugs.

In this work, our goal is to \emph{test what is being executed}. We present a new methodology for testing legacy distributed systems and uncovering bugs before these systems are released in the wild. We achieve this using \psharp~\cite{deligiannis2015psharp}, an extension of the mainstream language \csharp that provides two key capabilities: (i) a flexible way of modeling the environment using simple language features; and (ii) a systematic concurrency testing framework that is able to capture and take control of all the nondeterminism in a real system (together with its modeled environment) and systematically explore execution paths to discover bugs.

@@

>>>>

Distributed systems are notoriously hard to design, implement and test~\cite{cavage2013there, laguna2015debugging, maddox2015test}. This is due to many well-known sources of \emph{nondeterminism}~\cite{chandra2007paxos}, such as race conditions in the asynchronous interaction between system components, the use of multithreaded code inside a component, unexpected node failures, unreliable communication channels and data losses, and interaction with (human) clients.
%
All these sources of nondeterminism translate into \emph{exponentially} many execution paths that a distributed system might potentially execute. A bug might hide deep inside one of these paths and only manifest under extremely rare corner cases~\cite{gray1986computers, musuvathi2008finding}.\SCComment{I suggest we add "but the consequence can be catastrophic". Otherwise, why does such an extremely unlikely bug matter?}

Classic techniques that product groups employ to test, verify and validate their systems (such as code reviews, unit testing, stress testing and fault injection) are unable to capture and control all the aforementioned sources of nondeterminism \SCComment{my comment is similar to the one in the intro: do we claim that we capture all sources of nondet?}, which causes the most tricky bugs being missed during testing and only getting exposed after a system has been put in production. Discovering and fixing bugs in production, though, is bad for business as it can cost a lot of money and many dissatisfied customers. \SCComment{do we have a few real stories about the damages? They are helpful.}

We interviewed engineers from the Microsoft Azure team regarding the top problems in distributed system development, and the unified response \SCComment{change "unified response" to "consensus"?} was that the most critical problem today is how to improve \emph{testing coverage} to find bugs \emph{before} a system goes in production. The need for better testing techniques is not specific to Microsoft; other companies, such as Amazon and Google, publicly acknowledge~\cite{newcombe2015aws} that testing methodologies have to improve to be able to reason about the correctness of increasingly more complex distributed systems.

Amazon recently published an article~\cite{newcombe2015aws} that describes their use of TLA+~\cite{lamport1994temporal} to detect distributed system bugs and prevent them from reaching production. TLA+ is a powerful specification language for verifying distributed protocols, but it is unable to verify the code that is actually being executed. The implied assumption is that a model of the system will be verified, and then the programmers are responsible to match what was verified with the source code of the real system. Although many design bugs can be caught with this approach, there is \emph{no guarantee} that the real distributed system will be free of bugs.\SCComment{we want to avoid making a general point that TLA+ has no guarantee to find all bugs, because our approach cannot either. Instead, we should say something like "as we will show in the paper, many bugs we found are too subtle to be discovered without examining concrete implementations."}

In this work, our goal is to \emph{test what is being executed}. We present a new methodology for testing legacy distributed systems and uncovering bugs before these systems are released in the wild. We achieve this using \psharp~\cite{deligiannis2015psharp}, an extension of the mainstream language \csharp that provides two key capabilities: (i) a flexible way of modeling the environment using simple language features; and (ii) a systematic concurrency testing framework that is able to capture and take control of all the nondeterminism in a real system (together with its modeled environment) and systematically explore execution paths to discover bugs. \SCComment{my comment is similar to the one in the intro: do we claim that we capture all sources of nondet?}

@@

\SCComment{let me give my overall comments about the current version of the paper here. This set of case studies are really cool. The fact that our approach is proven to be effective clearly is the primary selling point of the paper. Reviewers will love the results we have.

About the writing, there may be 3 areas to improve:
(1) the word "we" is overloaded, because "we" play multiple roles in this work. "We" built \psharp; "we", as developers, designed the TableMigration system; "we", as testers, also take the responsibility to test the legacy Azure vNext system. The current writing doesn't clearly differentiate these roles, so readers may wonder how much work does it requires if they want to adopt the approach. 
(2) The intro makes me feel that we compare with existing logic reasoning approaches such as TLA+, and point out the limitation of TLA+. Until much later in the paper, I realize that our approach doesn't have any logic reasoning ingredient in it. I suggest that the intro makes it clear that our approach is complementary to TLA+, not a competing approach. We should avoid give a comparison with TLA+, because it is not an apple-to-apple comparison.
(3) Section 4 is the most important section about the approach. I feel that we spend too much text on section 4.3, which is about building the test harness. My concern is that readers' minds may be dominated by how we mocked all kinds of objects and override real methods by fake methods. They may feel that, in the end, we tested a highly simplified system. This is not true, because the extent manager is a REALLY complicated system (which is shown as a small box in fig.3). I suggest that we zoom into this system to explain why many things can go wrong and it is hard to test in a conventional manner.}

### 2015-09-03 methodology.tex
modified:   casestudies.tex 	modified:   intro.tex 	modified:   methodology.tex 	modified:   overview.tex 	modified:   paper.tex 	modified:   psharp.tex

A key capability of the \psharp runtime is that it can run in \emph{bug-finding mode}, where a embedded systematic testing engine captures and takes control of all sources of nondeterminism (such as event handler interleavings, failures, and client requests) in a \psharp program, and then systematically explores all possible executions to discover bugs.

@@

\item The top level asynchrony due to message passing, has to be exposed as event sending using the \psharp runtime API. If the communication layer is not based on message passing, then additional effort must be spend into refactoring the system to use message passing. This step allows the \psharp runtime to capture and control the message passing interleavings during systematic testing.

\item Any source of nondeterminism in the system or the environment (e.g. failures and timers), must be modeled using the \psharp \texttt{Nondet()} method. This method returns a nondeterministic boolean value that is controlled by the \psharp runtime and can be used to systematically inject ``nondeterministic'' events and for bug reproduction.
\end{enumerate}

@@

The \texttt{Environment} is essentially a ``god'' machine: it is the very first machine that is created; has a handle to all other machines in the harness; and includes the logic based on which the test harness will execute (e.g. how many nodes should be created, how many failures should occur, etc).

>>>>

A key capability of the \psharp runtime is that it can run in \emph{bug-finding mode}, where an embedded systematic testing engine captures and takes control of all sources of nondeterminism (such as event handler interleavings, failures, and client requests) in a \psharp program, and then systematically explores all possible executions to discover bugs.

@@

\item The top level asynchrony due to message passing, has to be exposed as event sending using the \psharp runtime API. If the communication layer is not based on message passing, then additional effort must be spent into refactoring the system to use message passing. This step allows the \psharp runtime to capture and control the message passing interleavings during systematic testing.

\item Any source of nondeterminism in the system or the environment (e.g. failures and timers), must be modeled using the \psharp \texttt{Nondet()} method. This method returns a nondeterministic boolean value \SCComment{why only Boolean? even a timer returns a Boolean value?} that is controlled by the \psharp runtime and can be used to systematically inject ``nondeterministic'' events and for bug reproduction.
\end{enumerate}

@@

The \texttt{Environment} is essentially a ``god'' machine: \SCComment{it is helpful to indicate this machine clearly in Fig.3. I think it is the dashed line box} it is the very first machine that is created; has a handle to all other machines in the harness; and includes the logic based on which the test harness will execute (e.g. how many nodes should be created, how many failures should occur \SCComment{why is the failure rate limited? is there a supporting evidence for the limit we set?}, etc).

### 2015-09-03 paper.tex
modified:   casestudies.tex 	modified:   intro.tex 	modified:   methodology.tex 	modified:   overview.tex 	modified:   paper.tex 	modified:   psharp.tex

\usepackage{color}
\newcommand{\SQComment}[1]{\textcolor{red}{Shaz: #1}}
\newcommand{\PDComment}[1]{\textcolor{blue}{Pantazis: #1}}
\newcommand{\MMComment}[1]{\textcolor{cyan}{Matt: #1}}

@@

We present a new methodology for systematically testing distributed systems. Our approach involves the use of \psharp, an extension of \csharp that combines a flexible environmental modeling approach with a concurrency testing framework, which can capture and systematically explore all sources of nondeterminism. We present two case studies of using \psharp to test production distributed systems inside Microsoft. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem. \PDComment{we now have many bugs in Matt's system too.}

@@

\section{Distributed Systems}
\label{sec:bg}

>>>>

\usepackage{color}
\newcommand{\SQComment}[1]{\textcolor{red}{Shaz: #1}}
\newcommand{\PDComment}[1]{\textcolor{blue}{Pantazis: #1}}
\newcommand{\MMComment}[1]{\textcolor{cyan}{Matt: #1}}
\newcommand{\SCComment}[1]{\textcolor{orange}{Shuo: #1}}

@@

We present a new methodology for systematically testing distributed systems. Our approach involves the use of \psharp, an extension of \csharp that combines a flexible environmental modeling approach with a concurrency testing framework, which can capture and systematically explore all sources of nondeterminism\SCComment{this paper mainly focuses on the nondet due to scheduling, right? There are other sources, e.g., arbitrary input, system call behavior, clock, random number, etc. I feel that "all sources" is perhaps an overclaim}. We present two case studies of using \psharp to test production distributed systems inside Microsoft. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time, as they did not have an effective way to reproduce it. \psharp uncovered the bug in a very small setting, which made it easy to examine traces, identify and fix the problem. \PDComment{we now have many bugs in Matt's system too.}

@@

\section{Distributed Systems \SCComment{change to "Distributed System Bugs"?}
\label{sec:bg}

### 2015-09-03 psharp.tex
small update
modified:   casestudies.tex 	modified:   intro.tex 	modified:   methodology.tex 	modified:   overview.tex 	modified:   paper.tex 	modified:   psharp.tex

We have implemented multiple schedulers inside the \psharp runtime: \emph{random}, \emph{depth-first-search (DFS)}, ..., \emph{PCT}. It is easy to create a new scheduler by implementing the \texttt{ISchedulingStrategy} interface exposed by the \psharp libraries. The interface exposes callbacks that are invoked by the \psharp runtime for taking decisions regarding which machine to schedule next, and can be used for developing both generic and application-specific schedulers, although we have experimented only with generic schedulers so far. Exposing an intuititive interface for creating new schedulers is inspired by previous work~\cite{desai2015tr}.

@@

One can imagine a liveness monitor as a \emph{thermometer}: as the program executes and the liveness property is not satisfied, the liveness monitor stays in the hot state, which infinitely raises the temperature. If the liveness property is ever satisfied, and thus the liveness monitor transitions to a cold state, the temperature is instantly reduced to normal levels. Encoding liveness properties using hot and cold states enables the programmer to specify arbitrary LTL properties. The liveness monitors in \psharp are based on previous work~\cite{?}.

@@

For \texttt{await}, no special treatment is required because \texttt{await} statements are compiled into a continuation. The task associated with the continuation will also be wrapped and scheduled accordingly.

>>>>

We have implemented multiple schedulers inside the \psharp runtime: \emph{random}, \emph{depth-first-search (DFS)}, ..., \emph{PCT}. It is easy to create a new scheduler by implementing the \texttt{ISchedulingStrategy} interface exposed by the \psharp libraries. The interface exposes callbacks that are invoked by the \psharp runtime for taking decisions regarding which machine to schedule next, and can be used for developing both generic and application-specific schedulers, although we have experimented only with generic schedulers so far. Exposing an intuitive interface for creating new schedulers is inspired by previous work~\cite{desai2015tr}.

@@

One can imagine a liveness monitor as a \emph{thermometer}: as the program executes and the liveness property is not satisfied, the liveness monitor stays in the hot state, which infinitely raises the temperature. If the liveness property is ever satisfied, and thus the liveness monitor transitions to a cold state, the temperature is instantly reduced to normal levels. Encoding liveness properties using hot and cold states enables the programmer to specify arbitrary LTL properties. The liveness monitors in \psharp are based on previous work~\cite{?}.\SCComment{at this point, I realize that our work (perhaps \psharp) doesn't have any symbolic reasoning ingredient in it, right? so the comparison with TLA+ is not an apple-to-apple comparison.}

@@

For \texttt{await} statements, no special treatment is required because \texttt{await} statements are compiled into a continuation. The task associated with the continuation will also be wrapped and scheduled accordingly.
